% ==================== 参考文献 ====================
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{参考文献}

\bibitem{nist80057} Barker E. Recommendation for Key Management, Part 1: General. NIST Special Publication 800-57 Part 1 Revision 5, 2020.

\bibitem{fips197} National Institute of Standards and Technology. Advanced Encryption Standard (AES). FIPS PUB 197, 2001.

\bibitem{dworkin2007gcm} Dworkin M. Recommendation for Block Cipher Modes of Operation: Galois/Counter Mode (GCM) and GMAC. NIST Special Publication 800-38D, 2007.

\bibitem{mcgrew2004gcm} McGrew D, Viega J. The Security and Performance of the Galois/Counter Mode (GCM) of Operation. In: Proceedings of INDOCRYPT, 2004: 343--355.

\bibitem{rogaway2002aead} Rogaway P. Authenticated-Encryption with Associated-Data. In: Proceedings of the 9th ACM Conference on Computer and Communications Security (CCS), 2002: 98--107.

\bibitem{rfc5116} McGrew D. An Interface and Algorithms for Authenticated Encryption. RFC 5116, IETF, 2008.

\bibitem{rfc2104} Krawczyk H, Bellare M, Canetti R. HMAC: Keyed-Hashing for Message Authentication. RFC 2104, IETF, 1997.

\bibitem{fips180} National Institute of Standards and Technology. Secure Hash Standard (SHS). FIPS PUB 180-4, 2015.

\bibitem{rfc7519} Jones M, Bradley J, Sakimura N. JSON Web Token (JWT). RFC 7519, IETF, 2015.

\bibitem{provos1999bcrypt} Provos N, Mazi\`eres D. A Future-Adaptable Password Scheme. In: Proceedings of the USENIX Annual Technical Conference, 1999.

\bibitem{rfc8018} Moriarty K, Kaliski B, Rusch A. PKCS \#5: Password-Based Cryptography Specification Version 2.1. RFC 8018, IETF, 2017.

\bibitem{sabt2015tee} Sabt M, Achemlal M, Bouabdallah A. Trusted Execution Environment: What It is, and What It is Not. In: IEEE Trustcom/BigDataSE/ISPA, 2015: 57--64.

\bibitem{costan2016sgx} Costan V, Devadas S. Intel SGX Explained. IACR Cryptology ePrint Archive, Report 2016/086, 2016.

\bibitem{mckeen2013sgx} McKeen F, Alexandrovich I, Berenzon A, et al. Innovative Instructions and Software Model for Isolated Execution. In: Proceedings of the 2nd International Workshop on Hardware and Architectural Support for Security and Privacy (HASP), 2013.

\bibitem{anati2013attestation} Anati I, Gueron S, Johnson S, Scarlata V. Innovative Technology for CPU Based Attestation and Sealing. In: Proceedings of HASP, 2013.

\bibitem{pinto2019trustzone} Pinto S, Santos N. Demystifying Arm TrustZone: A Comprehensive Survey. ACM Computing Surveys, 2019, 51(6): 1--36.

\bibitem{fips203} National Institute of Standards and Technology. Module-Lattice-Based Key-Encapsulation Mechanism Standard. FIPS PUB 203, 2024.

\end{thebibliography}
